Look, we can do something

### 2024-11-11 paper.tex
More images

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary. Although the resulting algorithm will
have the same $O(n^2)$ complexity, doing so can increase computational time
significantly. We call the parameter $P'$ with $d_{AB}$ in the place of
$\rho_{AB}$ ``improved awesomeness''.

>>>>

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary (see \cref{fig:improved}). Although the
resulting algorithm will have the same $O(n^2)$ complexity, doing so can
increase computational time significantly. We call the parameter $P'$ with
$d_{AB}$ in the place of $\rho_{AB}$ ``improved awesomeness''. The following
relation always holds: $0 < P \le P' \le 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/improved.png}
  \caption[]{Pairs of points responsible for \highlight{awesomeness} (red) and
    improved \highlight{awesomeness} (green).}
  \label{fig:improved}
\end{figure}
